\chapter{Introduction}\label{ch:intro}
%these sections are optional, up-to the author
\section{Motivation}
 Perhaps everyone knows that the whole modern world is a giant virtual web. The times when the exchange of information was carried out on the principle of "from hand to hand", and the main data carrier was a stamped paper folder, are in the distant past, but now countless virtual highways connect all points of the planet into a single information system – a computer data transmission network.         
  
  Among all of the essentials for human existence, the need to interact with others ranks just below our need to sustain life. Communication is almost as important to us as our reliance on air, water, food, and shelter.

   In today’s world, through the use of networks, we are connected like never before. People with ideas can communicate instantly with others to make those ideas a reality. News events and discoveries are known worldwide in seconds. Individuals can even connect and play games with friends separated by oceans and continents.

   Advancements in networking technologies are perhaps the most significant changes in the world today. They are helping to create a world in which national borders, geographic distances, and physical limitations become less relevant, presenting ever-diminishing obstacles.

   The internet has changed the manner in which our social, commercial, political, and personal interactions occur. The immediate nature of communications over the internet encourages the creation of global communities. Global communities allow for social interaction that is independent of location or time zone.
   
   The creation of online communities for the exchange of ideas and information has the potential to increase productivity opportunities across the globe.
   The creation of the cloud lets us store documents and pictures and access them anywhere, anytime. So whether we are on a train, in a park, or standing on top of a mountain, we can seamlessly access our data and applications on any device.
 
  We think that our website will help students change the world.






















\section{Aims and Objectives}
 
 What is the purpose of this project?
   In today’s world, through the use of networks, we are connected like never before. People with ideas can communicate instantly with others to make those ideas a reality. The creation of online communities for the exchange of ideas and information has the potential to increase productivity opportunities across the globe. The creation of the cloud lets us store documents and pictures and access them anywhere, anytime. Our goal is to create a website for learning Computer networks. The site will have educational materials, laboratory work and quizzes.

What are the problems it will solve?
  Currently, at the university, we use the official Cisco netacad websites for training. And the answers of laboratory work and quizzes are on the Internet. We want to create laboratories for students to solve problems themselves and solve quizzes to attach their knowledge.

What is the product vision? 
  Our programs teach the skills and disciplines necessary for learning.













\section{Thesis Outline}

   Our project structure, in the first part, we consider and say about stimulus to do this project and our aims and goals for doing this project
